Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-11 paper/paper.tex
Bug in generic fixpoint definition.
Spelled out the meaning of join.
The semantics is also parameterized by join.

Compared with the standard machine semantics, this definition is
different in the following ways:
\begin{itemize}
\item the store maps addresses to \emph{sets} of values,
\item continuations are heap-allocated,
\item there are ``contour values'' (written $\mcntr$) and syntax
  labels ($\mlab$) threaded through the computation, and
\item the machine is implicity parameterized by the functions
  $\mathit{push}$, $\mathit{bind}$, and $\interpdelta$.
\end{itemize}

@@

\begin{align*}
\mathit{push}_\mlab^\mcntr(\msto,\mkont) &=
  \mlab\mcntr,\msto\sqcup[\mlab\mcntr\mapsto\{\mkont\}] \\
\mathit{bind}^\mcntr_\mlab(\menv,\msto,\mvar,\mval) &= \menv[\mvar \mapsto \maddr],
                                           \msto\sqcup[\maddr \mapsto
                                             \{ \mval\}],
                                           \mcntr' \\
\mbox{where } \mcntr' &= \lfloor\mlab\mcntr\rfloor_k \\
              \maddr &= x\mcntr' \\
%%              \lfloor \mtcntr \rfloor_k &= \mtcntr \\
              \lfloor \mcntr \rfloor_0 &= \mtcntr \\
              \lfloor \mlab\mcntr \rfloor_{k+1} &= \mlab\lfloor \mcntr\rfloor_k
\end{align*}

@@

\begin{align*}
{\mathcal F}(f)(X) &= {\mathcal G}(f, X, \varnothing) \\
{\mathcal G}(f, \varnothing, S) &= S \\
{\mathcal G}(f, X, S) &= {\mathcal G}(f, f(X) \setminus S, S \cup f(X)) \\
\end{align*}

@@

\begin{align*}
(cs, \msto) &\widehat{\machstep} (cs', \msto') \\
\mbox{where } cs' &= \{c' \mid wn(c, \msto) \machstep wn(c, \msto^c), c \in cs\} \\
              \msto' &= \bigcup\{\msto^c \mid wn(c,\msto)\machstep wn(c', \msto^c), c \in cs\}
\end{align*}

>>>>

Compared with the standard machine semantics, this definition is
different in the following ways:
\begin{itemize}
\item the store maps addresses to \emph{sets} of values,
\item continuations are heap-allocated,
\item there are ``contour values'' (written $\mcntr$) and syntax
  labels ($\mlab$) threaded through the computation, and
\item the machine is implicity parameterized by the functions
  $\mathit{push}$, $\mathit{bind}$, $\interpdelta$ and $\sqcup$.
\end{itemize}

@@

\begin{align*}
\mathit{push}_\mlab^\mcntr(\msto,\mkont) &=
  \mlab\mcntr,\msto\sqcup[\mlab\mcntr\mapsto\{\mkont\}] \\
\mathit{bind}^\mcntr_\mlab(\menv,\msto,\mvar,\mval) &= \menv[\mvar \mapsto \maddr],
                                           \msto\sqcup[\maddr \mapsto
                                             \{ \mval\}],
                                           \mcntr' \\
\mbox{where } \mcntr' &= \lfloor\mlab\mcntr\rfloor_k \\
              \maddr &= x\mcntr' \\
%%              \lfloor \mtcntr \rfloor_k &= \mtcntr \\
              \lfloor \mcntr \rfloor_0 &= \mtcntr \\
              \lfloor \mlab\mcntr \rfloor_{k+1} &= \mlab\lfloor \mcntr\rfloor_k
\end{align*}
For the duration of this paper, $\sqcup$ is a pointwise lifting of $\cup$:
\begin{align*}
\msto\sqcup \varnothing &= \msto \\
\msto\sqcup \msto'[\maddr \mapsto S] &= \lambda \maddralt. \left\{ 
  \begin{array}{ll}
    \msto(\maddr)\cup S & \mbox{if } \maddralt = \maddr, \maddr\in dom(\msto) \\
    S & \mbox{if } \maddralt = \maddr, \maddr\notin dom(\msto) \\
    (\msto\sqcup\msto')(\maddralt) & \mbox{otherwise}
  \end{array}\right.
\end{align*}

@@

\begin{align*}
{\mathcal F}(f)(X) &= {\mathcal G}(f, X, \varnothing) \\
{\mathcal G}(f, \varnothing, S) &= S \\
{\mathcal G}(f, X, S) &= {\mathcal G}(f, f(X) \setminus S, S \cup X) \\
\end{align*}

@@

\begin{align*}
(cs, \msto) &\widehat{\machstep} (cs', \msto') \\
\mbox{where } cs' &= \{c' \mid wn(c, \msto) \machstep wn(c, \msto^c), c \in cs\} \\
              \msto' &= \bigsqcup\{\msto^c \mid wn(c,\msto)\machstep wn(c', \msto^c), c \in cs\}
\end{align*}
